Labelling Panels in R

### 2013-10-22 _knitr-posts/2013-10-21-panel-letters.Rmd
Add "R" to panel post
Add pos as argument to function

---
layout: post
title: Labelling Plot Panels
subtitle: Strategies for placing letters in figure panels.
---

@@

```{r}
#' @param xfrac The fraction over from the left side.
#' @param yfrac The fraction down from the top.
#' @param label The text to label with.
#' @param ... Anything extra to pass to text(), e.g. cex, col.
add_label <- function(xfrac, yfrac, label, ...) {
  u <- par("usr")
  x <- u[1] + xfrac * (u[2] - u[1])
  y <- u[4] - yfrac * (u[4] - u[3])
  text(x, y, label, pos = 4, ...)
}
```

>>>>

---
layout: post
title: Labelling Panels in R
subtitle: Strategies for placing letters in figure panels.
---

@@

```{r}
#' @param xfrac The fraction over from the left side.
#' @param yfrac The fraction down from the top.
#' @param label The text to label with.
#' @param pos Position to pass to text()
#' @param ... Anything extra to pass to text(), e.g. cex, col.
add_label <- function(xfrac, yfrac, label, pos = 4, ...) {
  u <- par("usr")
  x <- u[1] + xfrac * (u[2] - u[1])
  y <- u[4] - yfrac * (u[4] - u[3])
  text(x, y, label, pos = pos, ...)
}
```
